### 2021-03-03 paper.Rmd
more notes

Similarly, parallel coordinates plots (PCP) can be used to explore correlation and co-linearities in multivariate data [@Inselberg1985-kf]. In PCPs, variables are arranged along the (vertical) horizontal axis with vertical (horizontal) axes drawn representing the range of values for each variable. Points (observations) of the data are represented by drawing lines between each variables axis. If there is positive correlation between two variables the lines will be parallel, while for negative correlation the lines will cross. By placing multiple variables side by side in a PCP higher order structure like clustering or lower dimensional embeddings is revealed, however the ordering of variables is important to reveal these features. <!-- anything else? Andrew's curves etc.? -->

<!-- Original tours (Di)
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
(picture of the cluster data from Stuart's thesis)
- Alternatives (Stuart) 
-->

@@

1D: `display_hist`: histogram
2D: `display_xy`, recent development `display_sage()` - will be detailed in the last section @Transformations on projections (Ursula)

>>>>

Similarly, parallel coordinates plots (PCP) can be used to explore correlation and co-linearities in multivariate data [@Inselberg1985-kf]. In PCPs, variables are arranged along the (vertical) horizontal axis with vertical (horizontal) axes drawn representing the range of values for each variable. Points (observations) of the data are represented by drawing lines between each variables axis. If there is positive correlation between two variables the lines will be parallel, while for negative correlation the lines will cross. By placing multiple variables side by side in a PCP higher order structure like clustering or lower dimensional embeddings is revealed, however the ordering of variables is important to reveal these features. <!-- anything else? Andrew's curves etc., heat? -->

<!-- Original tours (Di)
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
(picture of the cluster data from Stuart's thesis)
- Alternatives (Stuart) 
  - cluster heatmaps 
  - data pipelines (?)
  - point to other reviews
- What do we mean by multivariate data visualisation?
- multivariate categorical vis, tree maps etc.
- subplots trellis literature
-->

@@

1D: `display_hist`: histogram
2D: `display_xy`, recent development `display_sage()` - will be detailed in the last section Transformations on projections (Ursula)
